\section*{Bibliografía}
\printbibliography[heading=bibintoc]


Abadi, D., Boncz, P., Harizopoulos, S., Idreos, S., y Madden, S. (2012). The Design and Implementation of Modern Column-Oriented Database Systems. Foundations and Trends in Databases, 5(3): 197–280.\\

Abadi, D. J., Madden, S. R., y Hachem, N. (2008). Column-Stores vs. Row-Stores: How Different Are They Really? Trabajo presentado en 28th ACM SIGMOD/PODS International Conference on Management of Data / Principles of Database Systems, Vancouver, BC, Canada.\\

Kimball, Ralph and Ross, Margy. 2002. The data warehouse toolkit : the complete guide to dimensional modeling. Second Edition. s.l. : Wiley Computer Publishing, 2002. ISBN 0-471- 20024-7\\

La Gran Enciclopedia de Economía. 2009. Definición de compra. La Gran Enciclopedia de Economía. [En línea] Economía48.com, 2009. [Citado el: 18 de 10 de 2012.] http://www.economia48.com/spa/d/compra/compra.htm.
\begin{itemize}
\item 2009. La Gran Enciclopedia de Economía. [En línea] Economía48.com, 2009. [Citado el: 18 de 10 de 2013.] http://www.economia48.com/spa/d/inventario/inventario.htm.
\end{itemize}

Russo, M., Ferrari, A., y Webb, C. (2012). Microsoft SQL Server 2012 Analysis Services: The BISM Tabular Model. United States of America: O’Reilly\\

Turner, Hammond, y Cotton. (1979). A DBMS for Large Statistical Database. Trabajo presentado en VLDB Conference (Very Large Data Base Endowment), Rio de Janeiro, Brazil.\\

Vitt, Liz y Cameron, Scott. 2012. Choosing a Tabular or Multidimensional Modeling Experience in SQL Server 2012 Analysis Services. [En línea] 2012. [Citado el: 22 de Noviembre de 2012.] http://msdn.microsoft.com/en-us/library/hh994774.aspx

